Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-27 paper/paper.tex
Conclusion paragraph

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
L-HS 1960   & Velocity potential       & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and energy         & Yes & Yes & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
L-H 1987    & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
H 1988      & Hamiltonian              & Yes & Yes & No  & Analytical \\
\hline
ZM 1990     & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
PAG 2021    & Crest and action         & Yes & No & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes* & No  & Analytical \\
            & conservation             &     &      &     & and numerical \\
\hline
\end{tabular}
\caption{
  Summary of prior
  \citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
  *: long 3rd order Stokes wave is considered only in numerical simulations.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

@@

In this paper we revisited the problem of short-wave modulation by long waves
from a linear wave theory perspective.
Using the linearized wave crest and action conservation equations, coupled with
the nonlinear gravity modulation for short waves that includes the the curvature
effects of the long wave, we derived new analytical solutions for the modulation
of short wave wavenumber, amplitude, steepness, intrinsic frequency, and phase
speed.
The latter two have not been previously examined in the context of short-wave
modulation, but are important for correctly calculating the wind input into
short waves, which is proportional to the wind speed relative to the wave
celerity.

>>>>

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
L-HS 1960   & Velocity potential       & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and energy         & Yes & Yes & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
L-H 1987    & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
H 1988      & Hamiltonian              & Yes & Yes & No  & Analytical \\
\hline
ZM 1990     & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
PAG 2021    & Crest and action         & Yes & No & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes & No  & Analytical \\
            & conservation             &     &     &     & and numerical \\
\hline
\end{tabular}
\caption{
  Summary of prior
  \citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

@@

In this paper we revisited the problem of short-wave modulation by long waves
from a linear wave theory perspective.
Using the linearized wave crest and action conservation equations, coupled with
the nonlinear gravity modulation for short waves that includes the the curvature
effects of the long wave, we derived new analytical solutions for the modulation
of short wave wavenumber, amplitude, steepness, intrinsic frequency, and phase
speed.
The latter two have not been previously examined in the context of short-wave
modulation, but are important for correctly calculating the wind input into
short waves, which is proportional to the wind speed relative to the wave
celerity.
The approximate steady solutions yield higher wavenumber and amplitude
modulation than that of \citet{longuet1960changes}, and somewhat lower than 
the numerical solutions of \citet{longuet1987propagation} and
\citet{zhang1990evolution}.
This is mainly due to the analytical solution requiring the crest and action
conservation equations to be linearized, and the nonlinearity arising only due
to the evaluation of short waves on the surface of the long wave (as opposed to
the mean water level) and due to nonlinear effective gravity.

The numerical solutions of the full wave crest and action conservation equations
are consistent with the analytical solutions for $\varepsilon_L < 0.2$.
The simulations also reveal that the unsteady growth of short-wave steepness
reported by \citet{peureux2021unsteady} is due to the sudden appearance of
long waves in a homogeneous short-wave field, a scenario that is unlikely to
occur in nature.
A more likely conditions, such as that of a long-wave groups, are only mildly
destabilizing for the short waves.
These results suggest that for mildly-to-moderately steep short waves,
the analytical steady solutions presented here are sufficient to describe the
modulation of short waves by long waves.
